Verifying Demonstrations

### 2017-07-26 properties.tex
Fixes typo
Adds notes from paper

\begin{frame}
  \begin{question}
    Are there other structures than block chains?
    E.g.~\cite{BlockchainFreeCryptocurrencies}.
  \end{question}
\end{frame}

@@

  \begin{question}
    How will this prevent us from reusing proofs from previous protests in 
    the same location(s)?
    (Related to V\ref{EligibilityVerif}.)
    What are the assumptions?
  \end{question}
  \begin{question}
    How hard is it to reuse old proofs?
  \end{question}
\end{frame}

@@

  \begin{question}
    How can we do \acp{LP} with 1000s of witnesses each?
    And then 1000s of such \acp{LP}?
  \end{question}
  \begin{question}
    Why should anyone trust these witnesses?
    What are the assumptions?
  \end{question}
\end{frame}

@@

  \begin{question}
    How to solve the Sybil problem?
  \end{question}
  \begin{question}
    This is similar to the double-spending problem for cryptocurrencies, can 
    we reuse any such techniques?
  \end{question}
\end{frame}

@@

\begin{frame}
  \begin{question}
    Will such a signature scheme solve both problems?
  \end{question}
  \begin{question}
    Is there such a signature scheme?
    Can we construct it?
  \end{question}
\end{frame}

>>>>

\begin{frame}
  \begin{question}
    Are there other structures than block chains?
    E.g.~\cite{BlockchainFreeCryptocurrencies}.
  \end{question}
  \begin{question}
    What about distributed voting/polling protocols?
    A tree should give a strict partial order?
  \end{question}
\end{frame}

@@

  \begin{question}
    How will this prevent us from reusing proofs from previous protests in 
    the same location(s)?
    What are the assumptions?
  \end{question}
  \begin{question}
    How hard is it to reuse old proofs?
    Forge all signatures due to changed values?
  \end{question}
\end{frame}

@@

  \begin{question}
    How can we do \acp{LP} with 1000s of witnesses each?
    And then 1000s of such \acp{LP}?
    Ad-hoc networks, broadcast \acp{LP}?
  \end{question}
  \begin{question}
    Why should anyone trust these witnesses?
    What are the assumptions?
    Signed over a short period of time?\footnote{%
      In a sense, if they collude they have shown support for the cause.
      As long as they are not Sybil it should be fine?
    }
  \end{question}
\end{frame}

@@

  \begin{question}
    How to solve the Sybil problem?
    Can we piggyback on existing \acp{PKI}?
    E.g.~\cite{Cinderella}.
  \end{question}
  \begin{question}
    This is similar to the double-spending problem for cryptocurrencies, can 
    we reuse any such techniques?
  \end{question}
\end{frame}

@@

\begin{frame}
  \begin{question}
    Will such a signature scheme solve both problems?
  \end{question}
  \begin{question}
    Is there such a signature scheme?
    Can we construct it?
  \end{question}
  \begin{question}
    What Alice submits her proof, stores the hash of the block, removes proof 
    and signature key?
  \end{question}
\end{frame}

From a computational-complexity perspective, operations that must be done on 
the phone must be cheap, other operations may be expensive.
